### 2023-06-05 proofs/tex/solution-merge-lemmas.tex
WIP: finish merge lemmas

\begin{lemma} [Soundness of Merge of Unification Solution Entries]
    \label{lemma:unif-sol-ent-merge-soundness}
    For a fixed context $[[Γ]]$,
    suppose that  $[[Γ ⊢ usEntry1]]$ and $[[Γ ⊢ usEntry2]]$,
    where $[[Γ ⊢ usEntryi]]$ is an equivalence-shaped restriction
    (i.e. it has shape $[[α̂⁺ :≈ iP]]$ or $[[α̂⁻ :≈ iN]]$ but not $[[α̂⁺ :≥ iP]]$).
    If $[[usEntry1 & usEntry2]]$ is defined then
    \begin{enumerate}
    \item $[[Γ ⊢ usEntry1 & usEntry2]]$
    \item $[[Γ ⊢ usEntry1 & usEntry2 ⇒ usEntry1]]$
    \item $[[Γ ⊢ usEntry1 & usEntry2 ⇒ usEntry2]]$
    \end{enumerate}
\end{lemma}
\begin{proof}
    Let us consider the rule forming $[[Γ ⊢ usEntry1 & usEntry2 = usEntry]]$.
    \begin{caseof}
        \item \ruleref{\ottdruleSMEPEqEqLabel}, i.e. 
        $[[Γ ⊢ usEntry1 & usEntry2 = usEntry]]$
        has form $[[Γ ⊢ (pua :≈ iP) & (pua :≈ iP') = (pua :≈ iP)]]$
        and $[[nf(iP) = nf(iP')]]$. Then
         \begin{enumerate}
            \item $[[Γ ⊢ usEntry]]$, i.e. $[[Γ ⊢ pua :≈ iP]]$ holds by assumption;
            \item $[[Γ ⊢ (pua :≈ iP) ⇒ (pua :≈ iP)]]$ holds by reflexivity (\cref{lemma:entry-weakening-preorder});
            \item $[[Γ ⊢ (pua :≈ iP) ⇒ (pua :≈ iP')]]$ holds
            because $[[nf(iP) = nf(iP')]]$ implies $[[Γ ⊢ iP ≈ iP']]$
            (by \cref{lemma:subt-equiv-algorithmization}), and thus, 
            \ruleref{\ottdruleSImpEPEqEqLabel} applies.
         \end{enumerate}
        \item \ruleref{\ottdruleSMENEqEqLabel}. The negative case is proved in exactly the same way.
    \end{caseof}
\end{proof}

\begin{lemma} [Soundness of Merge of Unification Solutions]
    \label{lemma:unif-sol-merge-soundness}
    Suppose that $[[us1 : Θ | varset1]]$ and $[[us2 : Θ | varset2]]$ 
    are unification solutions (i.e. $[[us1]]$ and $[[us2]]$ can only have equivalence-shaped restrictions).
    If $[[us1 & us2]]$ is defined then
    \begin{enumerate}
        \item $[[us1 & us2 : Θ|varset1 ∪ varset2]]$,
        \item $[[Θ|varset1 ⊢ us1 & us2 ⇒ us1]]$, and
        \item $[[Θ|varset2 ⊢ us1 & us2 ⇒ us2]]$.
    \end{enumerate}
\end{lemma}
\begin{proof}
    Let us prove the properties separately:
    \begin{enumerate}
        \item $[[us1 & us2 : Θ|varset1 ∪ varset2]]$.
        It suffices to prove the following two properties:
        \begin{itemize}
            \item The set of variables of the entries of $[[us1 & us2]]$ 
            coincides with $[[varset1 ∪ varset2]]$\\
            By definition, $[[us1 & us2]]$ consists of three parts:
            entries of $[[us1]]$ that do not have matching entries of $[[us2]]$,
            entries of $[[us2]]$ that do not have matching entries of $[[us1]]$,
            and the merge of matching entries.
            It means that $[[dom(us1 & us2)]] = [[dom(us1) \ dom(us2) ∪ dom(us2) \ dom(us1) ∪ 
            dom(us1) ∩ dom(us2)]] = [[dom(us1) ∪ dom(us2)]]$, which, since 
            $[[usi : Θ | varseti]]$, is equal to $[[varset1 ∪ varset2]]$.

            \item Each entry of $[[us1 & us2]]$ restricting $[[α̂±]]$ is well-formed in
            the corresponding context $[[Θ(α̂±)]]$.\\
            Let us consider an arbitrary entry $[[usEntry]]$ of $[[us1 & us2]]$ restricting
            $[[α̂±]]$. Then there are three cases:
            \begin{enumerate}
                \item $[[usEntry]]$ the entry is from $[[us1]]$ and does not have a matching entry 
                in $[[us2]]$, i.e. $[[α̂±]] \in [[dom(us1) \ dom(us2)]]$.
                Then $[[usEntry]]$ is well-formed in $[[Θ | varset1]]$ by assumption.
                \item $[[usEntry]]$ the entry is from $[[us2]]$ and does not
                have a matching entry in $[[us1]]$. This case is symmetric.
                \item $[[usEntry]]$ is the merge of two matching entries $[[usEntry1]] \in [[us1]]$
                 and $[[usEntry2]] \in [[us2]]$ restricting $[[α̂±]]$.
                 Since $[[us1 : Θ | varset1]]$ and $[[us2 : Θ | varset2]]$,
                 $[[α̂±]] \in [[dom(Θ|varset1) ∩ dom(Θ|varset2)]]$, i.e. there 
                 is an entry $[[ α̂±[Γ] ]] \in [[Θ]]$, and 
                 $[[usEntry1]]$ and $[[usEntry2]]$ are well-formed in $[[Γ]]$.
                 Then by \cref{lemma:unif-sol-ent-merge-soundness}, 
                 $[[Γ ⊢ usEntry1 & usEntry2]]$, where $[[Γ]] = [[Θ(α̂±)]]$.
            \end{enumerate}
        \end{itemize}
        \item $[[Θ|varset1 ⊢ us1 & us2 ⇒ us1]]$
        We need to show that for every entry $[[usEntry]]$ from $[[us1]]$,
        there is an entry $[[usEntry']]$ from $[[us1 & us2]]$ such that
        $[[Θ|varset1 ⊢ usEntry' ⇒ usEntry]]$. 
        Let us consider an arbitrary $[[usEntry]]$ from $[[us1]]$ restricting $[[α̂±]]$.
        Then there are two cases:
        \begin{itemize}
            \item $[[usEntry]]$ does not have a matching entry in $[[us2]]$.
            Then $[[usEntry]]$ is also in $[[us1 & us2]]$ and $[[Θ|varset1 ⊢ usEntry ⇒ usEntry]]$ 
            by reflexivity (\cref{lemma:entry-weakening-preorder}).
            \item $[[usEntry]]$ has a matching entry $[[usEntry']]$ in $[[us2]]$.
            Then $[[usEntry & usEntry']]$ is in $[[us1 & us2]]$ and $[[Θ|varset1 ⊢ usEntry & usEntry' ⇒ usEntry]]$ by \cref{lemma:unif-sol-ent-merge-soundness}.
        \end{itemize}
        \item $[[Θ|varset2 ⊢ us1 & us2 ⇒ us2]]$ is proved analogously.
    \end{enumerate}
\end{proof}

\begin{lemma} [Soundness of Solution Entry Merge]
\label{lemma:entry-merge-soundness}
For a fixed context $[[Γ]]$,
suppose that  $[[Γ ⊢ usEntry1]]$ and $[[Γ ⊢ usEntry2]]$. 
If $[[usEntry1 & usEntry2]]$ is defined then
\begin{enumerate}
    \item $[[Γ ⊢ usEntry1 & usEntry2]]$
    \item $[[Γ ⊢ usEntry1 & usEntry2 ⇒ usEntry1]]$
    \item $[[Γ ⊢ usEntry1 & usEntry2 ⇒ usEntry2]]$
\end{enumerate}
\end{lemma}
\begin{proof}
    Let us consider the rule forming $[[Γ ⊢ usEntry1 & usEntry2 = usEntry]]$.
    \begin{caseof}
        \item \ruleref{\ottdruleSMEPEqEqLabel} or \ruleref{\ottdruleSMENEqEqLabel}
        The proof is analogous to the proof of \cref{lemma:unif-sol-ent-merge-soundness}.
        \item \ruleref{\ottdruleSMESupSupLabel} 
        Then $[[usEntry1]]$ is $[[pua :≥ iP1]]$, $[[usEntry2]]$ is $[[pua :≥ iP2]]$,
        and $[[usEntry1 & usEntry2]]$ is $[[pua :≥ iQ]]$ where $[[iQ]]$ is the least upper bound of $[[iP1]]$ and $[[iP2]]$.
        Then by \cref{lemma:lub-soundness},
        \begin{itemize}
            \item $[[Γ ⊢ iQ]]$, and hence $[[Γ ⊢ pua :≥ iQ]]$, that is $[[Γ ⊢ usEntry1 & usEntry2]]$,
            \item $[[Γ ⊢ iQ ≥ iP1]]$, and hence $[[Γ ⊢ pua :≥ iQ ⇒ pua :≥ iP1]]$, that is $[[Γ ⊢ usEntry1 & usEntry2 ⇒ usEntry1]]$,
            \item $[[Γ ⊢ iQ ≥ iQ1]]$, and hence $[[Γ ⊢ usEntry1 & usEntry2 ⇒ usEntry2]]$.
        \end{itemize}
        \item \ruleref{\ottdruleSMESupEqLabel}
        Then $[[usEntry1]]$ is $[[pua :≥ iP]]$, $[[usEntry2]]$ is $[[pua :≈ iQ]]$, 
        where $[[Γ;· ⊨ uQ ≥ iP ⫤ us']]$, and the resulting   
        $[[usEntry1 & usEntry2]]$ is equal to $[[usEntry2]]$, that is $[[pua :≈ iQ]]$.

@@

\begin{lemma} [Soundness of Solution Merge] \label{lemma:merge-soundness}
    Suppose that $[[us1 : Θ1]]$ and $[[us2 : Θ2]]$ 
    and $[[us1 & us2]]$ is defined.
    Then 
    \begin{enumerate}
        \item $[[us1 & us2 : Θ1 ∪ Θ2]]$,
        \item $[[Θ1 ⊢ us1 & us2 ⇒ us1]]$, and
        \item $[[Θ2 ⊢ us1 & us2 ⇒ us2]]$.
    \end{enumerate}
\end{lemma}
\begin{proof}
    The proof repeats the proof of \cref{lemma:unif-sol-merge-soundness},
    but uses \cref{lemma:entry-merge-soundness} instead of 
    \cref{lemma:unif-sol-ent-merge-soundness}.
\end{proof}

\begin{lemma} [Completeness of Unification Solution Entry Merge]
    \label{lemma:unif-entry-merge-completeness}
    For a fixed context $[[Γ]]$,
    suppose that  $[[Γ ⊢ usEntry1]]$ and $[[Γ ⊢ usEntry2]]$, 
    where $[[Γ ⊢ usEntryi]]$ are equivalence-shaped restrictions.
    Suppose there exists an equivalence-shaped restriction 
    $[[Γ ⊢ usEntry]]$ such that $[[Γ ⊢ usEntry ⇒ usEntry1]]$ and $[[Γ ⊢ usEntry ⇒ usEntry2]]$.
    Then $[[usEntry1 & usEntry2]]$ is defined and
    $[[Γ ⊢ usEntry ⇒ usEntry1 & usEntry2]]$.
\end{lemma}
\begin{proof}
    By the soundness of unification solution entry merge (\cref{lemma:unif-sol-ent-merge-soundness}),
    Since the restrictions are equivalence-shaped, 
    the only possible rules inferring the weakening judgments are
    the positive \ruleref{\ottdruleSImpEPEqEqLabel} and the negative \ruleref{\ottdruleSImpENEqEqLabel}.
    Since $[[usEntry1]]$, $[[usEntry2]]$, and $[[usEntry]]$ 
    have the same polarity, we consider the positive case,
    and the negative case is proved analogously.

    Let us assume that $[[usEntry1]]$ is $[[pua :≈ iP1]]$,
    $[[usEntry2]]$ is $[[pua :≈ iP2]]$, $[[usEntry]]$ is $[[pua :≈ iQ]]$.
    Then by inversion of \ruleref{\ottdruleSImpEPEqEqLabel},
    \begin{itemize}
        \item $[[Γ ⊢ iQ ≈ iP1]]$, and hence $[[nf(iQ) = nf(iP1)]]$ by \cref{lemma:subt-equiv-algorithmization},
        \item $[[Γ ⊢ iQ ≈ iP2]]$, and hence $[[nf(iQ) = nf(iP2)]]$ by \cref{lemma:subt-equiv-algorithmization},
    \end{itemize}
    which implies $[[nf(iP1) = nf(iP2)]]$.
    It means that the merge of $[[usEntry1]]$ and $[[usEntry2]]$ is defined by \ruleref{\ottdruleSMEPEqEqLabel}:
    $[[Γ ⊢ (pua :≈ iP1) & (pua :≈ iP2) = (pua :≈ iP1)]]$.

    To show that $[[Γ ⊢ (pua :≈ iQ) ⇒ (pua :≈ iP1)]]$, we apply \ruleref{\ottdruleSImpEPEqEqLabel}:
    $[[Γ ⊢ iP1 ≈ iQ]]$ is obtained from $[[Γ ⊢ iQ ≈ iP1]]$ by symmetry of equivalence.
\end{proof}

\begin{lemma} [Completeness of Unification Solution Merge] 
    \label{lemma:unif-sol-merge-completeness}
    Suppose that $[[us1 : Θ|varset1]]$ and $[[us2 : Θ|varset2]]$ 
    are equivalence-only unification solutions
    and there exists $[[us]]$
    such that $[[Θ ⊢ us ⇒ us1]]$ and $[[ Θ ⊢ us ⇒ us2]]$.
    Then $[[us1 & us2]]$ is defined and 
    $[[ Θ ⊢ us ⇒ us1 & us2 ]]$.
\end{lemma}
\begin{proof}
    By  definition, $[[us1 & us2]]$ is a union of entries of $[[us1]]$, which do not have matching entries in $[[us2]]$,
    entries of $[[us2]]$, which do not have matching entries in $[[us1]]$, and the merge of matching entries.
    It is clear that the first two components of this union exist. Let us show that the third component exists, 
    i.e. that for every two entries $[[usEntry1]] \in [[us1]]$ and $[[usEntry2]] \in [[us2]]$
    restricting the same variable $[[α̂±]]$, $[[usEntry1 & usEntry2]]$ is defined.

    $[[Θ|varset1 ⊢ us ⇒ us1]]$ means that there exists $[[usEntry]] \in [[us]]$ restricting $[[α̂±]]$ such that
    $[[Θ(α̂±) ⊢ usEntry ⇒ usEntry1]]$. Similarly, since there can be only one entry in $[[usEntry]]$ restricting 
    the same variable$[[α̂±]]$, $[[Θ2 ⊢ us ⇒ us2]]$ means $[[Θ(α̂±) ⊢ usEntry ⇒ usEntry2]]$.
    Then by \cref{lemma:unif-sol-ent-merge-soundness}, $[[usEntry1 & usEntry2]]$ is defined and 
    $[[Θ(α̂±) ⊢ usEntry ⇒ usEntry1 & usEntry2]]$.

\begin{lemma} [Completeness of Solution Entry Merge]
    \label{lemma:entry-merge-completeness}
    For a fixed context $[[Γ]]$,
    suppose that  $[[Γ ⊢ usEntry1]]$ and $[[Γ ⊢ usEntry2]]$.
    Suppose there exists an entry $[[Γ ⊢ usEntry]]$ such that $[[Γ ⊢ usEntry ⇒ usEntry1]]$ and $[[Γ ⊢ usEntry ⇒ usEntry2]]$.
    Then $[[usEntry1 & usEntry2]]$ is defined and
    $[[Γ ⊢ usEntry ⇒ usEntry1 & usEntry2]]$.
\end{lemma}
\begin{proof}
    Notice that $[[usEntry1]]$, $[[usEntry2]]$, and $[[usEntry]]$
    restrict the same variable and have the same polarity. If the polarity is negative,
    then the proof is analogous to the proof of \cref{lemma:unif-entry-merge-completeness}.

    Let us consider the shape of $[[usEntry]]$.
    \begin{caseof}
        \item $[[usEntry]]$ is $[[pua :≥ iP]]$.
        \label{case:entry-merge-completeness-sup-sup}
         Then the only rule inferring 
        $[[Γ ⊢ usEntry ⇒ usEntryi]]$ is \ruleref{\ottdruleSImpESupSupLabel}.
        This way, $[[usEntry1]]$ is $[[pua :≥ iP1]]$ and $[[usEntry2]]$ is $[[pua :≥ iP2]]$,
        and $[[iP]]$ is a common supertype of $[[iP1]]$ and $[[iP2]]$, i.e. $[[Γ⊢ iP ≥ iP1]]$ and $[[Γ ⊢ iP ≥ iP2]]$.
        Then by \cref{lemma:lub-completeness}, $[[iP1 ∨ iP2]]$ is defined and $[[Γ ⊢ iP ≥ iP1 ∨ iP2]]$.
        Then $[[usEntry1 & usEntry2]]$, that is $[[pua :≥ iP1 & pua :≥ iP1]]$, is defined as 
        $[[pua :≥ iP1 ∨ iP2]]$ by \ruleref{\ottdruleSMESupSupLabel}.
        Moreover, $[[Γ ⊢ usEntry ⇒ usEntry1 & usEntry2]]$, that is $[[Γ ⊢ pua :≥ iP ⇒ pua :≥ iP1 ∨ iP2]]$,
        holds by \ruleref{\ottdruleSImpESupSupLabel}.

@@

\begin{lemma} [Completeness of Solution Merge] 
    \label{lemma:merge-completeness}
    Suppose that $[[us1 : Θ|varset1]]$ and $[[us2 : Θ|varset2]]$
    and there exists $[[us]]$
    such that $[[Θ ⊢ us ⇒ us1]]$ and $[[Θ ⊢ us ⇒ us2]]$.
    Then $[[us1 & us2]]$ is defined and 
    $[[ Θ ⊢ us ⇒ us1 & us2]]$.
\end{lemma}
\begin{proof}
    The proof is analogous to the proof of \cref{lemma:unif-sol-merge-completeness}.
    The only difference is that we use \cref{lemma:entry-merge-completeness} instead of
    \cref{lemma:unif-entry-merge-completeness}.
\end{proof}

>>>>

\begin{lemma} [Soundness of Solution Entry Merge]
\label{lemma:entry-merge-soundness}
For a fixed context $[[Γ]]$,
suppose that  $[[Γ ⊢ usEntry1]]$ and $[[Γ ⊢ usEntry2]]$. 
If $[[usEntry1 & usEntry2]]$ is defined then
\begin{enumerate}
    \item $[[Γ ⊢ usEntry1 & usEntry2]]$
    \item $[[Γ ⊢ usEntry1 & usEntry2 ⇒ usEntry1]]$
    \item $[[Γ ⊢ usEntry1 & usEntry2 ⇒ usEntry2]]$
\end{enumerate}
\end{lemma}
\begin{proof}
    Let us consider the rule forming $[[Γ ⊢ usEntry1 & usEntry2 = usEntry]]$.
    \begin{caseof}
        \item \ruleref{\ottdruleSMEPEqEqLabel}, i.e. 
        $[[Γ ⊢ usEntry1 & usEntry2 = usEntry]]$
        has form $[[Γ ⊢ (pua :≈ iP) & (pua :≈ iP') = (pua :≈ iP)]]$
        and $[[nf(iP) = nf(iP')]]$. Then
         \begin{enumerate}
            \item $[[Γ ⊢ usEntry]]$, i.e. $[[Γ ⊢ pua :≈ iP]]$ holds by assumption;
            \item $[[Γ ⊢ (pua :≈ iP) ⇒ (pua :≈ iP)]]$ holds by reflexivity (\cref{lemma:entry-weakening-preorder});
            \item $[[Γ ⊢ (pua :≈ iP) ⇒ (pua :≈ iP')]]$ holds
            because $[[nf(iP) = nf(iP')]]$ implies $[[Γ ⊢ iP ≈ iP']]$
            (by \cref{lemma:subt-equiv-algorithmization}), and thus, 
            \ruleref{\ottdruleSImpEPEqEqLabel} applies.
         \end{enumerate}
        \item \ruleref{\ottdruleSMENEqEqLabel} the negative case is proved in exactly the same way as the positive one.
        \item \ruleref{\ottdruleSMESupSupLabel} 
        Then $[[usEntry1]]$ is $[[pua :≥ iP1]]$, $[[usEntry2]]$ is $[[pua :≥ iP2]]$,
        and $[[usEntry1 & usEntry2]]$ is $[[pua :≥ iQ]]$ where $[[iQ]]$ is the least upper bound of $[[iP1]]$ and $[[iP2]]$.
        Then by \cref{lemma:lub-soundness},
        \begin{itemize}
            \item $[[Γ ⊢ iQ]]$, and hence $[[Γ ⊢ pua :≥ iQ]]$, that is $[[Γ ⊢ usEntry1 & usEntry2]]$,
            \item $[[Γ ⊢ iQ ≥ iP1]]$, and hence $[[Γ ⊢ pua :≥ iQ ⇒ pua :≥ iP1]]$, that is $[[Γ ⊢ usEntry1 & usEntry2 ⇒ usEntry1]]$,
            \item $[[Γ ⊢ iQ ≥ iQ1]]$, and hence $[[Γ ⊢ usEntry1 & usEntry2 ⇒ usEntry2]]$.
        \end{itemize}
        \item \ruleref{\ottdruleSMESupEqLabel}
        Then $[[usEntry1]]$ is $[[pua :≥ iP]]$, $[[usEntry2]]$ is $[[pua :≈ iQ]]$, 
        where $[[Γ;· ⊨ uQ ≥ iP ⫤ us']]$, and the resulting   
        $[[usEntry1 & usEntry2]]$ is equal to $[[usEntry2]]$, that is $[[pua :≈ iQ]]$.

@@

\begin{lemma} [Soundness of Solution Merge] \label{lemma:merge-soundness}
    Suppose that $[[us1 : Θ1]]$ and $[[us2 : Θ2]]$ 
    and $[[us1 & us2]]$ is defined.
    Then 
    \begin{enumerate}
        \item $[[us1 & us2 : Θ1 ∪ Θ2]]$,
        \item $[[Θ1 ⊢ us1 & us2 ⇒ us1]]$, and
        \item $[[Θ2 ⊢ us1 & us2 ⇒ us2]]$.
    \end{enumerate}
\end{lemma}
\begin{proof}

    Let us prove the properties separately:
    \begin{enumerate}
        \item $[[us1 & us2 : Θ|varset1 ∪ varset2]]$.
        It suffices to prove the following two properties:
        \begin{itemize}
            \item The set of variables of the entries of $[[us1 & us2]]$ 
            coincides with $[[varset1 ∪ varset2]]$\\
            By definition, $[[us1 & us2]]$ consists of three parts:
            entries of $[[us1]]$ that do not have matching entries of $[[us2]]$,
            entries of $[[us2]]$ that do not have matching entries of $[[us1]]$,
            and the merge of matching entries.
            It means that $[[dom(us1 & us2)]] = [[dom(us1) \ dom(us2) ∪ dom(us2) \ dom(us1) ∪ 
            dom(us1) ∩ dom(us2)]] = [[dom(us1) ∪ dom(us2)]]$, which, since 
            $[[usi : Θ | varseti]]$, is equal to $[[varset1 ∪ varset2]]$.

            \item Each entry of $[[us1 & us2]]$ restricting $[[α̂±]]$ is well-formed in
            the corresponding context $[[Θ(α̂±)]]$.\\
            Let us consider an arbitrary entry $[[usEntry]]$ of $[[us1 & us2]]$ restricting
            $[[α̂±]]$. Then there are three cases:
            \begin{enumerate}
                \item $[[usEntry]]$ the entry is from $[[us1]]$ and does not have a matching entry 
                in $[[us2]]$, i.e. $[[α̂±]] \in [[dom(us1) \ dom(us2)]]$.
                Then $[[usEntry]]$ is well-formed in $[[Θ | varset1]]$ by assumption.
                \item $[[usEntry]]$ the entry is from $[[us2]]$ and does not
                have a matching entry in $[[us1]]$. This case is symmetric.
                \item $[[usEntry]]$ is the merge of two matching entries $[[usEntry1]] \in [[us1]]$
                 and $[[usEntry2]] \in [[us2]]$ restricting $[[α̂±]]$.
                 Since $[[us1 : Θ | varset1]]$ and $[[us2 : Θ | varset2]]$,
                 $[[α̂±]] \in [[dom(Θ|varset1) ∩ dom(Θ|varset2)]]$, i.e. there 
                 is an entry $[[ α̂±[Γ] ]] \in [[Θ]]$, and 
                 $[[usEntry1]]$ and $[[usEntry2]]$ are well-formed in $[[Γ]]$.
                 Then by \cref{lemma:entry-merge-soundness}, 
                 $[[Γ ⊢ usEntry1 & usEntry2]]$, where $[[Γ]] = [[Θ(α̂±)]]$.
            \end{enumerate}
        \end{itemize}
        \item $[[Θ|varset1 ⊢ us1 & us2 ⇒ us1]]$
        We need to show that for every entry $[[usEntry]]$ from $[[us1]]$,
        there is an entry $[[usEntry']]$ from $[[us1 & us2]]$ such that
        $[[Θ|varset1 ⊢ usEntry' ⇒ usEntry]]$. 
        Let us consider an arbitrary $[[usEntry]]$ from $[[us1]]$ restricting $[[α̂±]]$.
        Then there are two cases:
        \begin{itemize}
            \item $[[usEntry]]$ does not have a matching entry in $[[us2]]$.
            Then $[[usEntry]]$ is also in $[[us1 & us2]]$ and $[[Θ|varset1 ⊢ usEntry ⇒ usEntry]]$ 
            by reflexivity (\cref{lemma:entry-weakening-preorder}).
            \item $[[usEntry]]$ has a matching entry $[[usEntry']]$ in $[[us2]]$.
            Then $[[usEntry & usEntry']]$ is in $[[us1 & us2]]$ and $[[Θ|varset1 ⊢ usEntry & usEntry' ⇒ usEntry]]$ 
            by \cref{lemma:entry-merge-soundness}.
        \end{itemize}
        \item $[[Θ|varset2 ⊢ us1 & us2 ⇒ us2]]$ is proved analogously.
    \end{enumerate}
\end{proof}

\begin{lemma} [Completeness of Solution Entry Merge]
    \label{lemma:entry-merge-completeness}
    For a fixed context $[[Γ]]$,
    suppose that  $[[Γ ⊢ usEntry1]]$ and $[[Γ ⊢ usEntry2]]$.
    Suppose there exists an entry $[[Γ ⊢ usEntry]]$ such that $[[Γ ⊢ usEntry ⇒ usEntry1]]$ and $[[Γ ⊢ usEntry ⇒ usEntry2]]$.
    Then $[[usEntry1 & usEntry2]]$ is defined and
    $[[Γ ⊢ usEntry ⇒ usEntry1 & usEntry2]]$.
\end{lemma}
\begin{proof}

    Let us consider the shape of $[[usEntry]]$.
    \begin{caseof}

        \item $[[usEntry]]$ is $[[nua :≈ iM]]$
        Then since $[[usEntry1]]$, $[[usEntry2]]$, and $[[usEntry]]$
        restrict the same variable, they have the same polarity. 
        So $[[usEntry1]]$ is $[[nua :≈ iN1]]$, $[[usEntry2]]$ is $[[nua :≈ iN2]]$, 
        Then by inversion of \ruleref{\ottdruleSImpENEqEqLabel},
        \begin{itemize}
            \item $[[Γ ⊢ iM ≈ iN1]]$, and hence $[[nf(iM) = nf(iN1)]]$ by \cref{lemma:subt-equiv-algorithmization},
            \item $[[Γ ⊢ iM ≈ iN2]]$, and hence $[[nf(iM) = nf(iN2)]]$ by \cref{lemma:subt-equiv-algorithmization},
        \end{itemize}
        which implies $[[nf(iN1) = nf(iN2)]]$.
        It means that the merge of $[[usEntry1]]$ and $[[usEntry2]]$ is defined by \ruleref{\ottdruleSMENEqEqLabel}:
        $[[Γ ⊢ (nua :≈ iN1) & (nua :≈ iN2) = (nua :≈ iN1)]]$.

        To show that $[[Γ ⊢ (nua :≈ iM) ⇒ (nua :≈ iN1)]]$, we apply \ruleref{\ottdruleSImpENEqEqLabel}:
        $[[Γ ⊢ iN1 ≈ iM]]$ is obtained from $[[Γ ⊢ iM ≈ iN1]]$ by symmetry of equivalence.

        \item $[[usEntry]]$ is $[[pua :≥ iP]]$.
        \label{case:entry-merge-completeness-sup-sup}
         Then the only rule inferring 
        $[[Γ ⊢ usEntry ⇒ usEntryi]]$ is \ruleref{\ottdruleSImpESupSupLabel}.
        This way, $[[usEntry1]]$ is $[[pua :≥ iP1]]$ and $[[usEntry2]]$ is $[[pua :≥ iP2]]$,
        and $[[iP]]$ is a common supertype of $[[iP1]]$ and $[[iP2]]$, i.e. $[[Γ⊢ iP ≥ iP1]]$ and $[[Γ ⊢ iP ≥ iP2]]$.
        Then by \cref{lemma:lub-completeness}, $[[iP1 ∨ iP2]]$ is defined and $[[Γ ⊢ iP ≥ iP1 ∨ iP2]]$.
        Then $[[usEntry1 & usEntry2]]$, that is $[[pua :≥ iP1 & pua :≥ iP1]]$, is defined as 
        $[[pua :≥ iP1 ∨ iP2]]$ by \ruleref{\ottdruleSMESupSupLabel}.
        Moreover, $[[Γ ⊢ usEntry ⇒ usEntry1 & usEntry2]]$, that is $[[Γ ⊢ pua :≥ iP ⇒ pua :≥ iP1 ∨ iP2]]$,
        holds by \ruleref{\ottdruleSImpESupSupLabel}.

@@

\begin{lemma} [Completeness of Solution Merge] 
    \label{lemma:merge-completeness}
    Suppose that $[[us1 : Θ|varset1]]$ and $[[us2 : Θ|varset2]]$
    and there exists $[[us]]$
    such that $[[Θ ⊢ us ⇒ us1]]$ and $[[Θ ⊢ us ⇒ us2]]$.
    Then $[[us1 & us2]]$ is defined and 
    $[[ Θ ⊢ us ⇒ us1 & us2]]$.
\end{lemma}
\begin{proof}
    By  definition, $[[us1 & us2]]$ is a union of entries of $[[us1]]$, which do not have matching entries in $[[us2]]$,
    entries of $[[us2]]$, which do not have matching entries in $[[us1]]$, and the merge of matching entries.
    It is clear that the first two components of this union exist. Let us show that the third component exists, 
    i.e. that for every two entries $[[usEntry1]] \in [[us1]]$ and $[[usEntry2]] \in [[us2]]$
    restricting the same variable $[[α̂±]]$, $[[usEntry1 & usEntry2]]$ is defined.

    $[[Θ|varset1 ⊢ us ⇒ us1]]$ means that there exists $[[usEntry]] \in [[us]]$ restricting $[[α̂±]]$ such that
    $[[Θ(α̂±) ⊢ usEntry ⇒ usEntry1]]$. Similarly, since there can be only one entry in $[[usEntry]]$ restricting 
    the same variable$[[α̂±]]$, $[[Θ2 ⊢ us ⇒ us2]]$ means $[[Θ(α̂±) ⊢ usEntry ⇒ usEntry2]]$.
    Then by \cref{lemma:entry-merge-completeness}, $[[usEntry1 & usEntry2]]$ is defined and 
    $[[Θ(α̂±) ⊢ usEntry ⇒ usEntry1 & usEntry2]]$.
